\Title

### 2020-03-03 manuscript/manuscript.tex
Specify number of sources on manuscript

% Import files with parameter values generated by notebooks
\input{synthetic_model_surveys.tex}
\input{parameters_ground_survey.tex}
\input{parameters_airborne_survey.tex}
\input{best_parameters_ground_survey.tex}
\input{best_parameters_airborne_survey.tex}

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
    \caption{
        Source layouts.
        (a) Set of synthetic observation points that resemble a ground survey.
        (b) Location of sources obtained through the \emph{sources beneath
            data} layout.
        (c) Location of sources obtained through the \emph{block averaged
            sources} layout.
        (d) Location of sources obtained through the \emph{grid sources}
            layout.
    }
    \label{fig:source-layouts-schematics}
\end{figure*}

>>>>

% Import files with parameter values generated by notebooks
\input{synthetic_model_surveys.tex}
\input{parameters_ground_survey.tex}
\input{parameters_airborne_survey.tex}
\input{best_parameters_ground_survey.tex}
\input{best_parameters_airborne_survey.tex}
\input{source_layouts_schematics.tex}

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
    \caption{
        Source layouts.
        (a) Set of \SourceLayoutsSchematicsObservations{} synthetic observation
            points that resemble a ground survey.
        (b) Location of the \SourceLayoutsSchematicsSourceBellowData{} sources
            obtained through the \emph{sources beneath data} layout.
        (c) Location of the \SourceLayoutsSchematicsBlockMedianSources{}
            sources obtained through the \emph{block averaged sources} layout.
        (d) Location of the \SourceLayoutsSchematicsGridSources{} sources
            obtained through the \emph{grid sources} layout.
    }
    \label{fig:source-layouts-schematics}
\end{figure*}
